\section{Information}

\begin{distributions}[Statements]
The candidate will be \textbf{introduced} to
\begin{itemize}[leftmargin = *]
	\item	A variety of models (frequency, severity, and aggregate) useful for short-term actuarial applications.
	\item	A variety of tools for the calibration and evaluation of the models. 
	\item	The fundamental principles of pricing and reserving of some of the (more common) short-term insurance and reinsurance coverages.
\end{itemize}

The candidate will \textbf{learn and apply}
\begin{itemize}[leftmargin = *]
	\item	The steps to the modelling process.
\end{itemize}

The candidate should be \textbf{able to}:
\begin{enumerate}[leftmargin = *]
	\item	Analyse data from an applied business context.
	\item	Determine a suitable model and its parameter values.
	\item	Provide measures of confidence (for decisions based on the model).
	\item	Estimate losses using credibility procedures.
\end{enumerate}
\end{distributions}

\begin{outcomes}[Notes]
\begin{enumerate}[leftmargin = *]
	\item	The weights are provided to indicate the relative emphasis on different sections.
	\item	Some questions may cover multiple learning objectives.
\end{enumerate}
\end{outcomes}

Keyword in the learning objectives are coloured according to \href{https://cft.vanderbilt.edu/guides-sub-pages/blooms-taxonomy/}{\textcolor{black}{bloom's taxonomy here}}.
\begin{description}
	\item[\textcolor{amaranth}{create}]	develop, construct, investigate, assemble, etc.
	\item[\textcolor{amber}{evaluate}]	argue, defend, select, support, critique, etc.
	\item[\textcolor{applegreen}{analyse}]	organize, relate, compare, distinguish, examine, test, etc.
	\item[\textcolor{ao(english)}{apply}]	execute, solve, use, demonstrate, interpret, etc.
	\item[\textcolor{babyblue}{understand}]	classify, describe, discuss, explain, identify, recognize, select, etc.
	\item[\textcolor{blue(pigment)}{remember}]	define, list, memorize, repeat, state, etc.
\end{description}

\clearpage

\section{Autres ressources}
\begin{FORMULA_SUMM}{Links}
\begin{itemize}
	\item	\href{https://www.soa.org/education/exam-req/edu-exam-stam-detail/}{SOA site}.
\end{itemize}
\end{FORMULA_SUMM}