\chapter[Topic: General Cash Flows and Portfolios]{Topic: General Cash Flows and Portfolios (15\%-20\%)}

\subsection{Information}

\begin{distributions}[Objective]
The Candidate will understand key concepts concerning yield curves, rates of return, and measures of duration and convexity, and how to perform related calculations.
\end{distributions}

\begin{outcomes}[Learning outcomes]
The candidate will be able to:
\begin{enumerate}[label = \alph*)]
	\item	Define and recognize the \textit{definitions} of the following terms:
		\begin{multicols*}{2}
		\begin{itemize}[leftmargin = *]
		\item	Yield rate / rate of return;
		\item	Dollar-weighted rate of return;
		\item	Time-weighted rate of return;
		\item	Current value;
		\item	Duration	 (Macaulay and modified);
		\item	Convexity (Macaulay and modified);
		\item	Portfolio;
		\item	Spot rate;
		\item	Forward rate;
		\item	Yield Curve;
		\item	Stock price;
		\item	Stock dividend;
		\end{itemize}
		\end{multicols*}
	\item	Calculate:
		\begin{itemize}
		\item	The dollar-weighted and time-weighted rate of return;
		\item 	The duration and convexity of a set of cash flows;
		\item	Either Macaulay or modified duration given the other;
		\item	The approximate change in present value due to a change in interest rate,
			\begin{itemize}
			\item	Using 1st-order linear approximation based on modified duration;
			\item	Using 1st-order approximation based on Macaulay duration.
			\end{itemize}
		\item	The price of a stock using the dividend discount model;
		\item	The present value of a set of cash flows, using a yield curve developed from forward and spot rates.
		\end{itemize}
\end{enumerate}
\end{outcomes}

\begin{ASM_chapter}[Related lessons ASM]
Section 5: 
\begin{itemize}
	\item	\nameref{L.-5a}
	\item	\nameref{L.-5b}
	\item	\nameref{L.-5c}
	\item	\nameref{L.-5d}
	\item	\nameref{L.-5e}
	\item	\nameref{L.-5f}
\end{itemize}
Section 8: 
\begin{itemize}
	\item	\nameref{L.-8a}
	\item	\nameref{L.-8b}
	\item	\nameref{L.-8c}
\end{itemize}
Section 10: 
\begin{itemize}
	\item	\nameref{L.-10a}
	\item	\nameref{L.-10b}
	\item	\nameref{L.-10c}
	\item	\nameref{L.-10d}
	\item	\nameref{L.-10e}
	\item	\nameref{L.-10f}
	\item	\nameref{L.-10g}
\end{itemize}
Section 11: 
\begin{itemize}
	\item	\nameref{L.-11a}
\end{itemize}
\end{ASM_chapter}

\begin{YTB_vids}[Vidéos YouTube]
\begin{itemize}
	\item	
\end{itemize}
\end{YTB_vids}

\subsection{Résumés des chapitres}

\begin{CHPT_SUMM_AUTO}[label = {L.-5a}]{5a. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-5b}]{5b. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-5c}]{5c. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-5d}]{5d. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-5e}]{5e. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-5f}]{5f. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-8a}]{8a. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-8b}]{8b. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-8c}]{8c. }
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\subsection{Notes sur les vidéos YouTube}

%\begin{YTB_SUMM}[label = {}]{}
%\begin{itemize}
%	\item	
%\end{itemize}
%\end{YTB_SUMM}