\chapter[Asset Pricing Models]{Asset Pricing Models (5\% à 10\%)}

\subsection{Information}

\begin{distributions}[Objective]
The Candidate will understand different methods for the valuation of asset portfolios and explain their appropriateness in different situations.
\end{distributions}

\begin{outcomes}[Learning outcomes]
The Candidate will be able to:
\begin{enumerate}[label = \alph*)]
	\item	Explain the Capital Asset Pricing Model (CAPM).
		\begin{knowledge}[]
		\begin{itemize}
		\item	Recognize the assumptions and properties of CAPM.
		\item	Calculate the required return on a particular asset, a portfolio or a project using CAPM.
		\end{itemize}
		\end{knowledge}
	\item	Explain factor models.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Recognize the assumptions of a factor model for security returns.
		\item	Identify the expected return, factors, factor betas, and firm-specific components of a security from its factor equation.
		\item	Calculate the required return on a particular asset, a portfolio or a project using a single-factor and a multi-factor model.
		\end{itemize}
		\end{knowledge}
\end{enumerate}
\end{outcomes}


\begin{ASM_chapter}[Related lessons ASM]
\begin{itemize}
	\item	\nameref{L.-6}
	\item	\nameref{L.-7}
	\item	\nameref{L.-8}
\end{itemize}
\end{ASM_chapter}

\begin{YTB_vids}[Vidéos YouTube]
\begin{itemize}
	\item	\href{https://www.youtube.com/watch?v=fDz_DgDJD5g&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=58&t=0s}{Capital Asset Pricing Model}.
	\item	\href{https://www.youtube.com/watch?v=JyUBm9M7Wyw&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=58}{How to Calculate Cost of Equity using CAPM}.
	\item	\href{https://www.youtube.com/watch?v=Lvhu1w0gsvc&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=59}{Capital Asset Pricing Model Assumptions}.
	\item	\href{https://www.youtube.com/watch?v=fo0Ba9-GCts&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=60}{Jensen's Alpha}.
	\item	\href{https://www.youtube.com/watch?v=zYyzxXEO84Q&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=63&t=0s}{The Market Risk Premium}.
	\item	\href{https://www.youtube.com/watch?v=46oLXwClvkw&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=35}{Weighted Average Cost of Capital (WACC)}.
\end{itemize}
\end{YTB_vids}

\begin{YTB_SUMM}[label = {SQ-BASICS-ML-INTRO}]{\href{https://www.youtube.com/watch?v=fDz_DgDJD5g&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=58&t=0s}{Capital Asset Pricing Model}}
\begin{itemize}
	\item	The CAPM is \textcolor{teal}{a formula for calculating the} \textcolor{cyan}{expected return of a security} \textcolor{amethyst}{based on its systematic risk}.
		\begin{align*}
			{\color{teal}r_{i}}	
			&{\color{cyan}=}	{\color{amethyst}r_{f}} {\color{cyan}+} {\color{black}\beta_{i}} ({\color{orange}r_{m}} {\color{cyan}-} {\color{amethyst}r_{f}})
		\end{align*}
		\begin{itemize}
		\item	For example, 
		\end{itemize}
\end{itemize}
\end{YTB_SUMM}

\begin{YTB_SUMM}[label = {SQ-BASICS-ML-INTRO}]{\href{https://www.youtube.com/watch?v=Lvhu1w0gsvc&list=PL_KGEFWqEaTBbYDupRektHIMG0G9u-Ru-&index=59}{Capital Asset Pricing Model Assumptions}}
\begin{itemize}
	\item	Don't assume that any one person can influence the price of a security---they are price takers.
	\item	Assume homogeneous expectations.
	\item	Efficient portfolios---i.e., portfolios with highest return.
\end{itemize}
\end{YTB_SUMM}




\subsection{Résumés des chapitres}

\begin{CHPT_SUMM_AUTO}[label = {L.-6}]{6. Capital Asset Pricing Model (CAPM)}
	\begin{itemize}
		\item	
	\end{itemize}
	
\paragraph{Note}	Practice debt one, understood it less and the difference between the calculation for levered vs unlevered.
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-7}]{7. Cost of Capital}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-8}]{8. Behavioral Finance and Multifactor Models}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

