\chapter[Binomial Pricing Models]{Binomial Pricing Models (10\%)}

\subsection{Information}

\begin{distributions}[Objective]
The Candidate will understand how binomial trees can be used to approximate the prices of both European and American call and put options on various underlying assets.
\end{distributions}

\begin{outcomes}[Learning outcomes]
The Candidate will be able to:
\begin{enumerate}[label = \alph*)]
	\item	Explain the concept of no arbitrage and the risk-neutral approach to valuing derivatives securities.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Understand the concept of no arbitrage when comparing actual and synthetic calls, or when comparing actual and synthetic puts.
		\item	Understand the concepts underlying the risk-neutral approach to valuing derivatives securities in the context of the Binomial Option Pricing Model.
		\end{itemize}
		\end{knowledge}
	\item	Use the Binomial Option Pricing Model to calculate the value of European and American call and put options, along with the value of Asian and barrier options.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Price options under a one-period binomial model on a stock with no dividends.
		\item	Extend the binomial model to multi-period settings for pricing both European and American call and put options.
		\item	Extend the binomial model to other underlying assets, including stock indices with continuous dividends, currencies, and futures contracts.
		\end{itemize}
		\end{knowledge}
	\end{enumerate}
\end{outcomes}

\begin{ASM_chapter}[Related lessons ASM]
\begin{itemize}
	\item	\nameref{L.-19}
	\item	\nameref{L.-20}
	\item	\nameref{L.-21}
	\item	\nameref{L.-22}
\end{itemize}
%\tcblistof[\subsubsection*]{CHPT}{Chapitres}
\end{ASM_chapter}

\begin{YTB_vids}[Vidéos YouTube]
\begin{itemize}
	\item	
\end{itemize}
\end{YTB_vids}

\subsection{Résumés des chapitres}

\begin{CHPT_SUMM_AUTO}[label = {L.-19}]{19. Comparing Options}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-20}]{{20. Binomial Trees---Stock, One Period}}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-21}]{21. Binomial Trees---General}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-22}]{22. Binomial Trees: Understanding Early Exercice of Options}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\subsection{Notes sur les vidéos YouTube}

%\begin{YTB_SUMM}[label = {}]{}
%\begin{itemize}
%	\item	
%\end{itemize}
%\end{YTB_SUMM}