\chapter[Capital Structure]{Capital Structure (10\%)}

\subsection{Information}

\begin{distributions}[Objective]
The Candidate will understand the factors that a company has to consider when deciding its capital structure.
\end{distributions}

\begin{outcomes}[Learning outcomes]
The Candidate will be able to:
\begin{enumerate}[label = \alph*)]
	\item	Explain different methods to raise capital.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Understand the two main forms of financing: 
			\begin{itemize}
			\item	equity issues and 
			\item	debt issues.
			\end{itemize}
		\item	Understand the process by which a company raises capital including 
			\begin{itemize}
			\item	venture capital, 
			\item	IPOs, 
			\item	additional issues, and 
			\item	private placement.
			\end{itemize}
		\end{itemize}
		\end{knowledge}
	\item	Describe the effect of capital structure on a company.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Calculate the effect from changes in capital structure on a company’s overall value, equity beta, cost of debt, cost of equity, and weighted-average cost of capital, assuming the two Modigliani and Miller propositions hold. 
		\item	Understand the effect of corporate tax and costs of financial distress, including the threat of bankruptcy, on the capital structure of a company.
		\item	Understand the role of agency costs and asymmetric information in affecting a company’s array of financing choices.
		\end{itemize}
		\end{knowledge}
	\end{enumerate}
\end{outcomes}

\begin{ASM_chapter}[Related lessons ASM]
\begin{itemize}
	\item	\nameref{L.-9}
	\item	\nameref{L.-10}
	\item	\nameref{L.-11}
	\item	\nameref{L.-12}
	\item	\nameref{L.-13}
\end{itemize}
\end{ASM_chapter}

\begin{YTB_vids}[Vidéos YouTube]
\begin{itemize}
	\item	
\end{itemize}
\end{YTB_vids}

\subsection{Résumés des chapitres}

\begin{CHPT_SUMM_AUTO}[label = {L.-9}]{9. Capital Structure}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-10}]{10. The Effect of Taxes on Capital Structure}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-11}]{11. Other Factors Affecting Optimal Debt-Equity Ratio}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-12}]{12. Equity Financing}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-13}]{13. Debt Financing}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\subsection{Notes sur les vidéos YouTube}

%\begin{YTB_SUMM}[label = {}]{}
%\begin{itemize}
%	\item	
%\end{itemize}
%\end{YTB_SUMM}