\chapter[Investment Risk and Project Analysis]{Investment Risk and Project Analysis (10\% à 15\%)}

\subsection{Information}

\begin{distributions}[Objective]
The Candidate will understand different ways to measure investment risk and conduct project analysis using advanced techniques used in capital budgeting.
\end{distributions}

\begin{outcomes}[Learning outcomes]
The Candidate will be able to:
\begin{enumerate}[label = \alph*)]
	\item	Discuss the advantages and disadvantages of different measures of investment risk.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Understand the properties, advantages, and disadvantages of the following investment risk measures: 
			\begin{itemize}
			\item	variance, 
			\item	semi-variance, 
			\item	Value-at-Risk (VaR), and 
			\item	Tail Value-at-Risk (TVaR).
			\end{itemize}
		\item	Calculate the risk measures listed above in order to compare investment opportunities.
		\end{itemize}
		\end{knowledge}
	\item	Conduct risk analysis.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Understand the following methods to conduct risk analysis: 
			\begin{itemize}
			\item	sensitivity analysis, 
			\item	break-even analysis, 
			\item	scenario analysis, and 
			\item	Monte-Carlo simulation.
			\end{itemize}
		\item	Use a decision tree to model future outcomes and analyze real options embedded in a project.
		\end{itemize}
		\end{knowledge}
	\end{enumerate}
\end{outcomes}

\begin{ASM_chapter}[Related lessons ASM]
\begin{itemize}
	\item	\nameref{L.-2}
	\item	\nameref{L.-3}
	\item	\nameref{L.-30}
\end{itemize}
\end{ASM_chapter}

\begin{YTB_vids}[Vidéos YouTube]
\begin{itemize}
	\item	
\end{itemize}
\end{YTB_vids}

\subsection{Résumés des chapitres}

\begin{CHPT_SUMM_AUTO}[label = {L.-2}]{2. Project Analysis}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-3}]{3. Monte Carlo Simulation}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-30}]{30. Real Options}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\subsection{Notes sur les vidéos YouTube}

%\begin{YTB_SUMM}[label = {}]{}
%\begin{itemize}
%	\item	
%\end{itemize}
%\end{YTB_SUMM}
