\chapter[Option Greeks and Risk Management]{Option Greeks and Risk Management (10\% à 15\%)}

\subsection{Information}

\begin{distributions}[Objective]
The Candidate will understand the importance of Option Greeks and risk management techniques in forming hedged asset portfolios that include positions in both options and the underlying asset.
\end{distributions}

\begin{outcomes}[Learning outcomes]
The Candidate will be able to:
\begin{enumerate}[label = \alph*)]
	\item	Explain the calculation and use of option price partial derivatives.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Compute and interpret Option Greeks, including Delta, Gamma, Theta, Vega, Rho, and Psi.
		\item	Compute the elasticity, Sharpe ratio, and risk premium for both an individual option (call or put) and a portfolio consisting of both options of multiple types and the underlying stock.
		\item	Approximate option prices using Delta, Gamma, and Theta.
		\end{itemize}
		\end{knowledge}
	\item	Explain how to control risk by using options in a hedging context.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Perform delta hedging by calculating the quantities of option units and stock shares to hold, and whether those positions should be long or short. 
		\item	Perform gamma hedging by calculating the quantities of option units (of various types) and stock shares to hold, and whether those positions should be long or short.
		\end{itemize}
		\end{knowledge}
	\item	Apply options and other derivatives in the context of actuarial-specific risk management.
		\begin{knowledge}[]
		\begin{itemize}
		\item	Understand how life insurers use derivatives to hedge long-term risks from the asset portfolio.
		\item	Understand how P and C insurers use derivatives to hedge short-term risks from the liability portfolio.
		\item	Understand how investment guarantees can be formed from equity-linked insurance and annuities.
		\item	Understand how options are employed in both pension funding and asset/liability management.
		\end{itemize}
		\end{knowledge}
	\end{enumerate}
\end{outcomes}

\begin{ASM_chapter}[Related lessons ASM]
\begin{itemize}
	\item	\nameref{L.-25}
	\item	\nameref{L.-26}
	\item	\nameref{L.-31}
\end{itemize}
\end{ASM_chapter}

\begin{YTB_vids}[Vidéos YouTube]
\begin{itemize}
	\item	
\end{itemize}
\end{YTB_vids}

\subsection{Résumés des chapitres}

\begin{CHPT_SUMM_AUTO}[label = {L.-25}]{25. The Black-Scholes Formula: Greeks}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-26}]{26. Delta Hedging}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\begin{CHPT_SUMM_AUTO}[label = {L.-31}]{31. Actuarial Applications of Options}
	\begin{itemize}
		\item	
	\end{itemize}
\end{CHPT_SUMM_AUTO}

\subsection{Notes sur les vidéos YouTube}

%\begin{YTB_SUMM}[label = {}]{}
%\begin{itemize}
%	\item	
%\end{itemize}
%\end{YTB_SUMM}